---
title: "dplyr: Error in select - unused arguments"
subtitle: "Series: What Can Go Wrong in R"
author: "StatistikinDD"
date: "Presentation Created: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    chakra: libs/remark-latest.min.js
    lib_dir: libs
    css: ["xaringan-themer.css", "libs/_css/my_css.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: 16:9
---

```{r setup, include = FALSE}

options(htmltools.dir.version = FALSE)
# knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = "")
knitr::opts_chunk$set(echo = FALSE, comment = "")
xaringanthemer::style_mono_accent(title_slide_background_color = "#EDF4FB",
                                  title_slide_text_color = "#000000",
                                  base_font_size = "18px")
Sys.setenv(LANG = "en")
```

# dplyr's select: A Simple Use Case

```{r dplyr1, echo = TRUE, eval = FALSE}
library(dplyr)

mtcars %>% 
  select(hp, wt, am) %>%  #<<
  head()
```

```{r dplyr1b, message = FALSE, warning = FALSE}
library(dplyr)

mtcars %>% 
  select(hp, wt, am) %>% 
  head() %>% 
  knitr::kable()

```

---

# dplyr: Things Suddenly Go Wrong

```{r Boston, echo = TRUE, message = FALSE, warning = FALSE}

library(MASS)
head(Boston, n = 2) #<<
```

```{r dplyr-error1, echo = TRUE, eval = FALSE}
mtcars %>% 
  select(hp, wt, am) %>% #<<
  head()
```

.red[Error in select(., hp, wt, am) : unused arguments (hp, wt, am)]

---

# So <u>WHAT</u> Went Wrong?

Let's load the MASS package again ... and display the startup message this time.

```{r, echo = TRUE, message = TRUE}
detach(package:MASS, unload = TRUE)
library(MASS)
```

**A `select()` function is defined in the `MASS` package as well as in `dplyr`.**

---

# So What Can We Do?

* If we don't take any precautions:
  + the **order in which we load packages** is decisive!
  + the package **loaded last** takes precedence

* Load **all** packages at the start of your script, in the right order  
  *here: load `MASS` <u>before</u> `dplyr` (or `tidyverse`)*

* Better: Be more explicit about which package should take precedence
  + ***double colon notation***: `dplyr::select()`  
  *This may become tedious when we use many `dplyr` functions in our script.*
  + use `conflicted` package at the top of your script
  
```{r, echo = TRUE}
library(conflicted)
conflict_prefer("select", "dplyr")
```

---

class: center, middle

# Thanks!

### Youtube: StatistikinDD

### Twitter: @StatistikinDD

### github: fjodor

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

Thanks to **Yihui Xie** for *{knitr}* and *{xaringan}* and **Garrick Aden-Buie** for *{xaringanthemer}*.
