---
title: "Object of Type Closure is Not Subsettable"
subtitle: "Series: What Can Go Wrong in R"
author: "StatistikinDD"
date: "Presentation Created: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    chakra: libs/remark-latest.min.js
    lib_dir: libs
    css: ["xaringan-themer.css", "libs/_css/my_css.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: 16:9
---

```{r setup, include = FALSE}

options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE, comment = "")
xaringanthemer::style_mono_accent(title_slide_background_color = "#EDF4FB",
                                  title_slide_text_color = "#000000",
                                  base_font_size = "18px")
Sys.setenv(LANG = "en")
options(width = 45)
library(printr)
```

# Object of Type Closure is not Subsettable

.Large[.red[Error in ... : object of type 'closure' is not subsettable]]

--

## How Can This Error Arise?

### 1. Accidentally using .Large[`**[]**`] instead of .Large[`**()**`]
### 2. Accidentally accessing a non-existing object that happens to be a function

--

## And What is a `'closure'`?

---

# 1. Accidentally using .Large[`**[]**`] instead of .Large[`**()**`]

.pull-left[
## Producing the Error

```{r, echo = TRUE, error = TRUE}
x <- 1:5
mean[x] #<<
summary[x] #<<
head[mtcars, n = 2] #<<
```
]

--

.pull-right[
## Solved!

```{r, echo = TRUE, results = "hold"}
mean(x) #<<
summary(x) #<<
head(mtcars, n = 2) #<<
```

]

---

# 2. Accidentally Accessing a Non-Existing Object

.pull-left[
## Producing the Error

```{r, echo = TRUE, error = TRUE}
data <- mtcars
data[1, 1:3]
df[1, 1:3]   #<<
```

#### For Comparison:

```{r, echo = TRUE, error = TRUE}
my_df[1, 1:3] #<<
```

]

--

.pull-right[
## Solved!

* Use `data[]` instead of `df[]`
* What is special about `df`?

```{r, echo = TRUE, results = "hold"}
class(df)
typeof(df)
?df #<<
```

]

---

# All Right - So What is a `'Closure'`, Anyway?

.pull-left[
## Consider This Code ...
```{r closure, echo = TRUE, eval = FALSE}
a <- 3

f <- function() {
  a <- a + 1
}

a
f()
a
```

]

--

.pull-right[
## Let's Run the Code ...
```{r, ref.label = "closure"}
```

```{r, echo = TRUE, results = "hold"}
class(f)
typeof(f)
```
]

### Functions "enclose" their environment

--

.pull-left[
```{r assign, echo = TRUE, eval = FALSE}
a
a <- f()
a
```
]

--

.pull-right[
```{r, ref.label = "assign", results = "hold"}
```

]

---

class: center, middle

# Thanks!

### Youtube: StatistikinDD

### Twitter: @StatistikinDD

### github: fjodor

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

Thanks to **Yihui Xie** for *{knitr}* and *{xaringan}* and **Garrick Aden-Buie** for *{xaringanthemer}*.
